---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BIOS625HW3

<!-- badges: start -->
<!-- badges: end -->

The goal of BIOS625HW3 is to develop an R package implementing an existing R function, or a group of R functions that are closely related to each other.

## Installation

You can install the development version of BIOS625HW3 from [GitHub](https://github.com/) with:

``` r
# install.packages("BIOS625HW3")
devtools::install_github("chemotaxis890/BIOS625HW3")
```

## In-package Dataset

```{r example}
library(BIOS625HW3)
names(stroke)
```
Check out the help page for the `stroke` dataset using `?stroke`. This is an example data for you to test the functions in this package.


















You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure,echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
