---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BIOS625HW3

<!-- badges: start -->

<!-- badges: end -->

The goal of BIOS625HW3 is to develop an R package implementing an existing R function, or a group of R functions that are closely related to each other.

## Installation

You can install the development version of BIOS625HW3 from [GitHub](https://github.com/) with:

``` r
# install.packages("BIOS625HW3")
devtools::install_github("chemotaxis890/BIOS625HW3")
```

## In-package Dataset

```{r example}
library(BIOS625HW3)
names(stroke)
```

Check out the help page for the `stroke` data set using `?stroke`,which has a simple code book for each variable. This is a build-in data for you to test the functions in this package.

## Function in this package

Check out the help page for the `slr()` function using `?slr()`. It is a function that returns the result of a simple linear regression model of two numeric variables.

For example, to get the regression model of Fatalism on Depression using `slr()`:

```{r}
slr('Depression','Fatalism',stroke)
```
