---
title: "Introduction-to-BIOS625HW3"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction-To-BIOS625HW3}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(BIOS625HW3)
```

## Examples of how to use it

The package contains a build-in data set called "stroke", which contains variables to explore the relationship between stroke and depression, considering for other co-variates.

```{r}
names(stroke)
```

The `slr()` function is to simulate the `lm()` function but in a simpler way that:

1\. Only test for one input and one outcome.

2\. The variables of interest need to be numeric (i.e., not categorical variables).

3\. The variables shall not contain missing values, Inf, or NaN.

The function returns a list of seven objects, including coefficient table, R-squared, formula, F-statistics of the model fit.

Here is an example to test the effect of age on depression score:

```{r}
fitted <- slr('Depression','Age',stroke)
fitted$coefficient
```

```{r}
fitted$formula
```

## Check Correctness with lm output

```{r}
fitted.lm <- lm(Depression~Age, stroke)
#check coefficient
all.equal(as.numeric(fitted.lm$coefficients),
          fitted$coefficient[,1])
#check t-statistics
all.equal(as.numeric(summary(fitted.lm)$coefficients[,3]),
          fitted$coefficient[,2])
#check p-value
all.equal(as.numeric(summary(fitted.lm)$coefficients[,4]),
          fitted$coefficient[,3])
#check R-squared
all.equal(summary(fitted.lm)$r.squared,
          fitted$R_squared)
#check F-statistic
all.equal(as.numeric(summary(fitted.lm)$fstatistic[1]),
          fitted$F_statistic)
#check F-statistic df1
all.equal(as.numeric(summary(fitted.lm)$fstatistic[2]),
          fitted$F_df1)
#check F-statistic df2
all.equal(as.numeric(summary(fitted.lm)$fstatistic[3]),
          fitted$F_df2)
#check F-statistic p-value
fstat <- summary(fitted.lm)$fstatistic
pval <- pf(fstat[1], fstat[2], fstat[3], lower.tail=FALSE)
all.equal(as.numeric(pval),fitted$F_p_value)

```

## Benchmark the functions
```{r}
library(bench)
result <-  bench::mark(as.numeric(lm(Depression~Age, stroke)$coefficients),
                       slr('Depression','Age',stroke)$coefficient[,1])
result
```

